Efficient Coalition Formation for Web Services

### 2013-03-06 papers/coalition/coalition.tex
Changes

Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of O(2^22) which would made that impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.

>>>>

Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.
